Understanding GDP Relations to Crime in US Cities

### 2017-03-08 paper/paper.Rmd
added to resource
added to paper

@@

**NEED KEY FINDINGS**

@@

Our final dataset came out as a final CSV that included any city or metropolitan areas that were included in both the crime and GDP dataset. For each of these cities or metropolitan areas, we included the crime data for 2010-2015 and the GDP for 2010-2015. This came out to include _____**(how many rows did we end up with for our data?)** cities or metropolitan areas.

@@

@@

Goulas, Eleftherios, and Athina Zervoyianni. "Economic Growth and Crime: Does Uncertainty Matter?" Applied Economics Letters 20.5 (2013): 420-27. Web.

Roman, John. "The Puzzling Relationship Between Crime and the Economy." CityLab. The Atlantic, 23 Sept. 2013. Web. 05 Mar. 2017.

The Economist Online. "Falling Together." The Economist. The Economist Newspaper, 26 Sept. 2011. Web. 05 Mar. 2017.

>>>>

********** Marisa
The key findings of our research showed that a poisson regression showed no correlation between the GDP per person and crime per person in each metropolitan area with population as another independent variable. Between all of the years from 2010 to 2015, there was no significance between GDP per person, crime per person, and population of a metropolitan area for any compared years. From this, our contribution to society and information in general is that just looking at a metropolitan area's economy and population is not a good determining factor on the number of crimes permitted by person.

@@

@@

Our final dataset came out as a final CSV that included any city or metropolitan areas that were included in both the crime and GDP dataset. For each of these cities or metropolitan areas, we included the crime data for 2010-2015 and the GDP for 2010-2015. This came out to include 366 cities or metropolitan areas. We also added columns such as crime per person in each metropolitan area and gdp per person in each metropolitan area to run our analyses on.

@@

Another thing to note is that 
'violent crimes' is defined by four offenses: murder and nonnegligent manslaughter, rape, robbery, and aggravated assault. 
'property crimes' is defined by four offenses: burglary, larceny theft, motor vehicle theft, and arson.

@@

[3] Goulas, Eleftherios, and Athina Zervoyianni. "Economic Growth and Crime: Does Uncertainty Matter?" Applied Economics Letters 20.5 (2013): 420-27. Web.

[2] Roman, John. "The Puzzling Relationship Between Crime and the Economy." CityLab. The Atlantic, 23 Sept. 2013. Web. 05 Mar. 2017.

[1] The Economist Online. "Falling Together." The Economist. The Economist Newspaper, 26 Sept. 2011. Web. 05 Mar. 2017.

### 2017-03-08 resource/index.Rmd
added to paper

---
title: "Understanding GDP relations to Crime in US Cities"
author: "Kai Yoshino, Isabella Spaletta, Chrisopther Ross, Marisa Nanakul"
date: "March 6, 2017"
output: html_document
---

>>>>

---
title: "Understanding GDP Relations to Crime in US Cities"
author: "Kai Yoshino, Isabella Spaletta, Chrisopther Ross, Marisa Nanakul"
date: "March 6, 2017"
output: html_document
---
